Data Dictionary for Body Fat Raw Dataset

### 2024-12-02 other/datasheet/datadictionary.qmd
cleaned r code

---
title: "Data Dictionary for Body Fat Dataset"
author: 
  - Wendy Yuan
thanks: "Code and data are available at: https://github.com/kiwindyy/Body-Fat"
date: November 29, 2024
date-format: long
format: pdf
---
**Density**

@@

- Type: Numeric
- Description: Age of the individual in years.
- Values/Range: 20–81
- Units: Years
- Remarks: Reflects life stage, which influences body composition.

@@

- Type: Numeric
- Description: Measurement around the waist.
- Values/Range: 27.3–49.6
- Units: Centimeters (cm)
- Remarks: Assesses fat distribution, often paired with hip circumference.

@@

- Type: Numeric
- Description: Circumference of the knee.
- Values/Range: 33.5–46.0
- Units: Centimeters (cm)
- Remarks: Provides detail about lower-body structure and proportions.

@@

- Type: Numeric
- Description: Circumference around the ankle.
- Values/Range: 20.2–27.0
- Units: Centimeters (cm)
- Remarks: Reflects skeletal and soft tissue composition in the lower leg.

@@

- Type: Numeric
- Description: Circumference of the bicep (arm flexed).
- Values/Range: 25.6–39.1
- Units: Centimeters (cm)
- Remarks: Highlights upper-arm muscle and fat distribution.

@@

- Type: Numeric
- Description: Circumference of the forearm.
- Values/Range: 24.6–33.8
- Units: Centimeters (cm)
- Remarks: Provides information about lower-arm composition.

>>>>

---
title: "Data Dictionary for Body Fat Raw Dataset"
author: 
  - Wendy Yuan
thanks: "Code and data are available at: https://github.com/kiwindyy/Body-Fat"
date: November 29, 2024
date-format: long
format: pdf
---
**Density**

@@

- Type: Numeric
- Description: Age of the individual in years.
- Values/Range: 22–81
- Units: Years
- Remarks: Reflects life stage, which influences body composition.

@@

- Type: Numeric
- Description: Measurement around the waist.
- Values/Range: 27.3–49.6
- Units: Inches (in)
- Remarks: Assesses fat distribution, often paired with hip circumference.

@@

- Type: Numeric
- Description: Circumference of the knee.
- Values/Range: 33.0–46.0
- Units: Centimeters (cm)
- Remarks: Provides detail about lower-body structure and proportions.

@@

- Type: Numeric
- Description: Circumference around the ankle.
- Values/Range: 19.1–33.9
- Units: Centimeters (cm)
- Remarks: Reflects skeletal and soft tissue composition in the lower leg.

@@

- Type: Numeric
- Description: Circumference of the bicep (arm flexed).
- Values/Range: 24.8–39.1
- Units: Centimeters (cm)
- Remarks: Highlights upper-arm muscle and fat distribution.

@@

- Type: Numeric
- Description: Circumference of the forearm.
- Values/Range: 21.0–34.9
- Units: Centimeters (cm)
- Remarks: Provides information about lower-arm composition.
